The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step

### 2017-03-24 Moving temporal window - HESS/template.tex
Changing the structure of the Data and methods section.

	The study area is the upper Rh\^{o}ne catchment in Switzerland. Precipitation time series come from six automatic weather stations, viz., Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle (Fig. \ref{fig:map}) that are subject to various meteorological influences \citep{Horton2012}. The data were available at an hourly time step for 25~years (1982\textendash 2007) and were also obtained at a daily time step (from 6:00~UTC to 6:00~UTC the next day) for 47~years (1961\textendash 2008). Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed. The results will hereafter be presented arbitrarily for the Ulrichen station but are equivalent for all stations.

	Synoptic-scale variables, used as predictors, were extracted from the ERA-20C reanalysis dataset \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree. The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar. The main advantage of the ERA-20C is that it allows testing the relevance of the MTW at a 3h time step.

	\subsection{The considered analogue method}
	\label{sec:analog_method}

@@

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.2cm]{fig06.pdf}
		\end{center}
		\caption{Synthesis of the changes in the S1 criterion due to the MTW (with a 12~h, 6~h, and 3~h time step) for the Ulrichen station depending on the rank of the analogue. (a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24~h is the standard approach without MTW). (b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}
		\label{fig:changes_S1}
	\end{figure}

@@

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.1cm]{fig09.pdf}
		\end{center}
		\caption{Synthesis of the changes in the RMSE criterion due to the MTW for the Ulrichen station depending on the rank of the analogue. (a) Quantiles of the RMSE distributions with and without the MTW. (b) Quantiles of the relative improvements of the RMSE criterion when using the MTW.}
		\label{fig:changes_RMSE}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=5cm]{fig10.pdf}
		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
		\label{fig:changes_CRPS_precip_threshold}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig11.pdf}
		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
		\label{fig:hours_selection_per_season}
	\end{figure}

>>>>

	The study area is the upper Rh\^{o}ne catchment in Switzerland. Precipitation time series come from six automatic weather stations, viz., Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle (Fig. \ref{fig:map}) that are subject to various meteorological influences \citep{Horton2012}. The data were available at an hourly time step for 29~years (1982\textendash 2010) and were also obtained at a daily time step (from 6:00~UTC to 6:00~UTC the next day) for 50~years (1961\textendash 2010). Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed. The results will hereafter be presented arbitrarily for the Ulrichen station but are equivalent for all stations.

	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree, and MERRA-2, from NASA, with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree. The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar. ERA-20C is build by assimilating only surface observations, and is thus available on a long period (1900\textendash 2010). On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present). It is of interest to consider these two datasets, as they represent different kind of products and are thus an interesting basis to assess the relevance of a MTW. The specific advantages of ERA-20C is that it allows testing the relevance of the MTW at a 3h time step, and covers a long period. On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.

	\subsection{The considered analogue methods}
	\label{sec:analog_method}

@@

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{fig06.pdf}
		\end{center}
		\caption{Synthesis of the changes in the S1 criterion due to the MTW (with a 12~h, 6~h, and 3~h time step) for the Ulrichen station depending on the rank of the analogue. (a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24~h is the standard approach without MTW). (b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}
		\label{fig:changes_S1}
	\end{figure}

@@

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{fig09.pdf}
		\end{center}
		\caption{Synthesis of the changes in the RMSE criterion due to the MTW for the Ulrichen station depending on the rank of the analogue. (a) Quantiles of the RMSE distributions with and without the MTW. (b) Quantiles of the relative improvements of the RMSE criterion when using the MTW.}
		\label{fig:changes_RMSE}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig10.pdf}
		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
		\label{fig:changes_CRPS_precip_threshold}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=7.5cm]{fig11.pdf}
		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
		\label{fig:hours_selection_per_season}
	\end{figure}
